### 2013-09-05 Tex/chapters/results.tex
Kleine Tipp- und Formulierungsfehler behoben

    The bootstrapping method estimates the error \(\Delta \overline{\avg{O}}\)

@@

    scaling behavior might be expected. I.e.\ Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}

@@

            \caption[Examples of GG for different $\sigma$]
            {
                GG with periodic boundary conditions for different \(\sigma\).
                The number of edges increases from \subref{sfig:GG_sigma:0.00}
                to \subref{sfig:GG_sigma:0.01} significantly. Until \subref{sfig:GG_sigma:0.15}
                it increases and after that the number of edges decreases.
            }
            \label{fig:GG_sigma}
        \end{figure}\\
        The evolution of the RNG with increasing \(\sigma\) can be made plausible
        with the same arguments. Fig. \ref{fig:RNG_sigma}
        shows that for \(\sigma \lesssim 0.1\) the square lattice character is
        preserved -- no new edges arise and only a few existing edges vanish, which
        explains the plateau in the \(T_{c}\) diagram. With
        increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
        thus reducing the degree and consequently the corresponding value of \(T_{c}\).
        \begin{figure}[htbp]
            \centering
            \subfigure[][$\sigma = 0.09$]
            {
                \label{sfig:RNG_sigma:0.09}
                \includegraphics[width=0.30\textwidth]{images/RNG/out009}
            }
            \subfigure[][$\sigma = 0.15$]
            {
                \label{sfig:RNG_sigma:0.15}
                \includegraphics[width=0.30\textwidth]{images/RNG/out015}
            }
            \subfigure[][$\sigma = 0.21$]
            {
                \label{sfig:RNG_sigma:0.21}
                \includegraphics[width=0.30\textwidth]{images/RNG/out021}
            }

            \caption[Examples of RNG for different $\sigma$]
            {
                RNG with periodic boundary conditions for different \(\sigma\).
                \subref{sfig:RNG_sigma:0.09} has still almost the square lattice
                configuration of edges, which is why the plateau from Fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}
                exists. In the next two pictures one sees the fast disappearance
                of edges, chracteristic for the RNG for a set of randomly
                distributed points (i.e.\ Poisson process).
            }
            \label{fig:RNG_sigma}
        \end{figure}

        \clearpage

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plots Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
        \begin{figure}[htbp]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
        to be a linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\) the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &= \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

    \subsubsection{Course of the Critical Temperature with Fixed Coupling Constants}
    \label{appendix:fixedCoupling}
        A quick analysis of this model with fixed coupling constants \(J = 1\)
        (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
        for variable \(J\) with \(\alpha=0.5\). This suggests that the
        disappearance of the jump is a random special case for the function
        \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
        The simulations were carried out on \(L \in \{16,32,64\}\) lattices
        for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
        Also note that the degree \(K\) is
        the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        because it is obviously independent of \(J\).
        Further, note that for small values of \(\sigma < 0.3\), \(T_c / K\)
        obtained using the fixed coupling strength \(J=1\) coincides with
        \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
        dependent coupling strength, Eq.\ \ref{eq:coupling}.
        This can be expected from the approximate analytic statement presented
        in Sec.\ \ref{sssec:J}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]
            {
                \label{sfig:Tc:RNG_A0}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
            }
            \subfigure[][]
            {
                \label{sfig:Tc:GG_A0}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
            }

@@

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}\\
        Because Ref.\ \cite{Janke1994} gives for the DT with \(J=1\) a
        critical temperature of \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given},
        it can be compared to the obtained \(T_{c,GG} = 2.19\)
        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should be very
        similar to a Poisson distributed set of nodes.
        Note that while for the graph ensembles the relation
        \begin{equation}
            DT \supseteq GG \supseteq RNG
        \end{equation}
        holds (see Sec. \ref{ssec:graphtypes}), the relation for the
        critical points on these graphs
        \begin{equation}
            T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}
        \end{equation}
        is also true.
        Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
        was true for \(\alpha = 0.5\) in the preceding sections.
        This phenomenon is also known from percolation where the relation
        \(p_{c,DT} \ge p_{c,GG} \ge p_{c,RNG}\) holds for the percolation
        threshold \(p_c\) -- the critical point of the percolation problem.
        The fact that the subgraph hierachy can be translated to
        the sequence of \(p_c\) for the subgraphs, is known as the containment
        theorem \cite{fisher}.
        Possibly the containment theorem is also applicable on this kind of
        problem.

>>>>

    The bootstrap method estimates the error \(\Delta \overline{\avg{O}}\)

@@

    scaling behavior might be expected, i.e.\ Eq.\ \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}

@@

            \caption[Examples of GG for different $\sigma$]
            {
                GG with periodic boundary conditions for different \(\sigma\).
                The number of edges increases from \subref{sfig:GG_sigma:0.00}
                to \subref{sfig:GG_sigma:0.01} significantly. Until \subref{sfig:GG_sigma:0.15}
                it increases and after that the number of edges decreases.
            }
            \label{fig:GG_sigma}
        \end{figure}\\
        The evolution of the RNG with increasing \(\sigma\) can be made plausible
        with the same arguments. Fig. \ref{fig:RNG_sigma}
        shows that for \(\sigma \lesssim 0.1\) the square lattice character is
        preserved -- no new edges arise and only a few existing edges vanish, which
        explains the plateau in the \(T_{c}\) diagram. With
        increasing \(\sigma\), more and more edges vanish\footnote{See also \url{http://www.youtube.com/watch?v=rltzi15mTM4} for an animation.},
        thus reducing the degree and consequently the corresponding value of \(T_{c}\).
        \begin{figure}[htb]
            \centering
            \subfigure[][$\sigma = 0.09$]
            {
                \label{sfig:RNG_sigma:0.09}
                \includegraphics[width=0.30\textwidth]{images/RNG/out009}
            }
            \subfigure[][$\sigma = 0.15$]
            {
                \label{sfig:RNG_sigma:0.15}
                \includegraphics[width=0.30\textwidth]{images/RNG/out015}
            }
            \subfigure[][$\sigma = 0.21$]
            {
                \label{sfig:RNG_sigma:0.21}
                \includegraphics[width=0.30\textwidth]{images/RNG/out021}
            }

            \caption[Examples of RNG for different $\sigma$]
            {
                RNG with periodic boundary conditions for different \(\sigma\).
                \subref{sfig:RNG_sigma:0.09} has still almost the square lattice
                configuration of edges, which is why the plateau from Fig.\ \ref{fig:Tc}\subref{sfig:Tc:RNG}
                exists. In the next two pictures one sees the fast disappearance
                of edges, chracteristic for the RNG for a set of randomly
                distributed points (i.e.\ Poisson process).
            }
            \label{fig:RNG_sigma}
        \end{figure}
        \clearpage

    \subsubsection{Influence of the Coupling Constant on the Critical Temperature}%
    \label{sssec:J}
        However, note that the degree does not alone influence the behavior of \(T_c\).
        Further \(T_c\) depends on the coupling constant \(J\), which is
        obvious from Eqs.\ \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
        coupling constant in turn is depending on the length of the edges,
        which changes with \(\sigma\).
        Therefore  in Fig.\ \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
        the mean sum of the coupling constants to all neighbors
        \begin{equation}
            \avg{\sum_{\avg{i,j}} J_{ij}}
        \end{equation}
        is plotted. This is a number which should combine the dependence on
        the degree and the coupling constant. It is determined by summing
        over the edge weights of all edges connected to a node and averaging
        this value over all nodes. Alternatively it is the average edge weight
        of all edges of the graph multiplied by the degree \(\avg{J_{ij}} K\).
        The plots Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
        \begin{figure}[hbtp]
            \centering
            \subfigure[][]
            {
                \label{sfig:sumJ:RNG}
                \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
            }
            \subfigure[][]
            {
                \label{sfig:sumJ:GG}
                \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
            }

@@

            \caption[Critical Temperature Normalized by Mean Sum of the Coupling Constants]
            {
                Top: Mean sum of the coupling constants to all
                neighbors over different disorder parameters for
                \subref{sfig:sumJ:RNG} the RNG and
                \subref{sfig:sumJ:GG} the GG.
                Bottom: Critical temperatures normalized by mean sum of the
                coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
                disorder parameters for
                \subref{sfig:Tc_normJ:RNG} the RNG and
                \subref{sfig:Tc_normJ:GG} the GG.
            }
            \label{fig:TcJ}
        \end{figure}\\
        Though Eq.\ \eqref{eq:exactHCTc} shows that there does not have
        to be a linear connection between \(J\) and \(T_c\), the best guess
        is a linear connection, because this model is derived from the
        square lattice, where the connection is linear. Therefore, one
        normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
        Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
        jump on the GG arises again, but \(T_c\) is now monotonically
        decreasing with increasing disorder parameter \(\sigma\).
        %~ This is a strong hint, that the change of the \(T_c\) with changing
        %~ \(\sigma\) is in some way connected to \(J\) and \(K\) which is an
        %~ expected conclusion.\\
        Moreover the forms of both curves are quite similar, but the
        one for the RNG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}
        is generally lower and spans over a bigger temperature range than
        the curve of the GG in Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:GG}.
        Both graph types have a plateau at \(0 < \sigma < 0.1\). The conclusion
        is that small disorder has little influence on this normalized critical
        temperature.
        Also both graph types exhibit a steep decline after the plateau before
        they approach an asymptotic limit for \(\sigma \gg 1\).\\
        If one looks at the behavior of \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
        for \(\sigma \ll 1\) and consequently \(d_{ij} \approx 1\), the
        following approximation is valid.
        \begin{equation}
            \abs{1-d_{ij}} := \varepsilon \ll 1
        \end{equation}
        \begin{equation}
            J_{ij} = e^{\pm \alpha \varepsilon} \approx 1 \pm \varepsilon \mp \dots
        \end{equation}
        \begin{align}
            \avg{\sum_{\avg{i,j}} J_{ij}} &= \avg{\sum_{\avg{i,j}} (1 \pm \varepsilon)} \\
                                          &= \frac{1 \pm \varepsilon}{N} \sum_{\avg{i,j}} 1 \\
                                          &= K(1 \pm \varepsilon) \approx K
        \end{align}
        Therefore this normalization is independent of the choice of \(\alpha\)
        at small values of \(\sigma\). In Sec.\ \ref{appendix:fixedCoupling}
        in Fig.\ \ref{fig:Tc_deg_A0}\subref{sfig:Tc_norm_deg:RNG_A0}\subref{sfig:Tc_norm_deg:GG_A0}
        the values from Fig.\ \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
        are compared to \(T / K\) for \(\alpha = 0\).

    \subsubsection{Course of the Critical Temperature with Fixed Coupling Constants}
    \label{appendix:fixedCoupling}
        A quick analysis of this model with fixed coupling constants \(J = 1\)
        (i.e.\ \(\alpha=0\)) is performed. The results are displayed in Fig.\ \ref{fig:Tc_deg_A0}.
        The jump from \(\sigma=0\) to \(\sigma>0\) does not disappear as in Fig.\ \ref{fig:Tc_deg}
        for variable \(J\) with \(\alpha=0.5\). This suggests that the
        disappearance of the jump is a random special case for the function
        \(J_{ij}=e^{\alpha(1-d_{ij})}\) at \(\alpha=0.5\).\\
        The simulations were carried out on \(L \in \{16,32,64\}\) lattices
        for a subset of the \(\sigma\) and \(T\) used in the previous simulation.
        Also note that the degree \(K\) is
        the same used in \ref{fig:Tc}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}
        because it is obviously independent of \(J\).
        Further, note that for small values of \(\sigma\), \(T_c / K\)
        obtained using the fixed coupling strength \(J=1\) coincides with
        \(T_c / \avg{\sum_{\avg{i,j}}J_{ij}}\) obtained using the distance
        dependent coupling strength (see Eq.\ \ref{eq:coupling}).
        This can be expected from the approximate analytic statement presented
        in Sec.\ \ref{sssec:J}.
        \begin{figure}[htb]
            \centering
            \subfigure[][]
            {
                \label{sfig:Tc:RNG_A0}
                \includegraphics[width=0.45\textwidth]{plots/RNG_Tc_A0}
            }
            \subfigure[][]
            {
                \label{sfig:Tc:GG_A0}
                \includegraphics[width=0.45\textwidth]{plots/GG_Tc_A0}
            }

@@

            \caption[Critical Temperature and Critical Temperature Normalized by Degree of the Graph for Fixed Coupling Constants $J=1$]
            {
                Top: Critical Temperature \(T_c\) of the graph over different
                disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:deg:RNG} the RNG and
                \subref{sfig:deg:GG} the GG.
                Bottom: Critical temperatures normalized by degree \(K\) over
                different disorder parameters \(\sigma\) with fixed coupling constants \(J=1\) for
                \subref{sfig:Tc_norm_deg:RNG} the RNG and
                \subref{sfig:Tc_norm_deg:GG} the GG. The values of \(T_c / K\)
                are compared to those of \(T_c /  \avg{\sum_{\avg{i,j}}J_{ij}}\)
                from Sec.\ \ref{sssec:J}.
            }
            \label{fig:Tc_deg_A0}
        \end{figure}\\
        Ref.\ \cite{Janke1994} gives a critical temperature for the DT with \(J=1\)
        \(T_{c,DT} = 3.80\)\footnote{more precise: a value of \(\frac{1}{T_c} \approx 0.263\) is given}.
        It can be compared to the obtained \(T_{c,GG} = 2.19\)
        and \(T_{c,RNG} = 1.13\) for \(\sigma = 1.2\), which should
        ensure a set of nodes very similar to a Poisson process.
        Note that while for the graph ensembles the relation
        \begin{equation}
            DT \supseteq GG \supseteq RNG
        \end{equation}
        holds (see Sec. \ref{ssec:graphtypes}), the relation for the
        critical points on these graphs
        \begin{equation}
            T_{c,DT} \ge T_{c,GG} \ge T_{c,RNG}
        \end{equation}
        is also true.
        Also keep in mind that the relation \(T_{c,GG} \ge T_{c,RNG}\)
        was true for \(\alpha = 0.5\) in the preceding sections.
        This phenomenon is also known from percolation where the relation
        \(p_{c,DT} \ge p_{c,GG} \ge p_{c,RNG}\) holds for the percolation
        threshold \(p_c\) -- the critical point of the percolation problem.
        The fact that the subgraph hierachy can be translated to
        the sequence of \(p_c\) for the subgraphs, is known as the containment
        theorem \cite{fisher}.
        Possibly the containment theorem is also applicable on this kind of
        problem.
